The transition redshift as a probe of reionization

### 2019-08-13 paper/ms.tex
Add how avg Halpha I is computed

>>>>

We assume a linear relationship between H-$\alpha$ luminosity and star
formation rate \citep{1998ARA&A..36..189K}:
\beq \label{eq:LHalpha_SFR}
\begin{split}
L_{\Ha} &= 3.29\times10^{7} \left(\frac{\SFR}{1\,\Msun\,\yr^{-1}}\right) L_{\odot} \\
        &\equiv L_{0,\Ha} \left(\frac{\SFR}{1\,\Msun\,\yr^{-1}}\right)
\end{split}
\eeq
This relation is based on a Salpeter IMF and is calibrated towards local
galaxies. As discussed in \citet{2019MNRAS.487.5902K}, the reality of
$z\sim10$ galaxies may be slightly different\,--\,the IMF may be more top
heavy, and the metal-poor nature of a typical star will naturally produce more
ionizing photons. However, the escape of ionizing photons may be more
efficient at higher redshift, and the conventional relation assumes no escape.
\citet{2019MNRAS.487.5902K} provide a slightly shallower fitting form for the
$L_{\Ha}-\SFR$ relation based upon their simulations, but we choose to use the
conventional relation here.

We use a fitting formula for the SFRd calibrated upon galaxies from $z=0$ to
$8$ \citep{2014ARA&A..52..415M}
\beq \label{eq:sfrd}
\psi(z) = 0.015 \frac{(1+z)^{2.7}}{1+\left[(1+z)/2.9\right]^{5.6}}\,M_{\odot}\yr^{-1}\Mpc^{-3} \text{.}
\eeq
The comoving emissitivity of the \Ha{} line can then be readily computed as,
\beq \label{eq:Ha_emiss}
\epsilon_{\Ha}(z) = L_{0,\Ha} \psi(z)\text{.}
\eeq
The average specific intensity can be computed from the comoving emissitivity
as \citep{2011ApJ...741...70L,2013ApJ...768...15P},
\beq \label{eq:int_from_em}
\avg{I_{\Ha}}(z) = \frac{\epsilon_{\Ha}(z)}{4\pi\nu_{\text{rest},\Ha}} \frac{c}{H(z)}
\eeq
